SNIK Quiz: Automatic Generation of Multiple Choice Questionnaires about Information Management in Hospitals

### 2022-01-27 quiz.tex
Shorten to 5 pages. Extend template table.

\begin{table}[t]
\caption{Quiz question templates.}
\label{tab:templates}
\centering
\begin{tabulary}{\columnwidth}{lL}
\toprule
\textbf{Template}	&\textbf{Description}\\
\midrule
\textbf{Definition}		&Ask for the class that fits the given textbook definition.\\
Example					&What is defined as \enquote{Examination of in and out patients in radiological department}?\\
Distractors				&Labels of other classes (that have a path of length 2 or less to the correct class.)\\
\midrule
\textbf{Subject}		&Ask for the class that is related via a given relation to a given object.\\
						&Key: Who is \emph{involved in} a \emph{healthcare network}?\\
Example					&Stem: \\
Distractors				&Labels of other classes (of the same type) that \emph{are not} related via the same relation to the same object, for example .\\
\midrule
\textbf{Intertwined}	&\\
						&Stem: \\
Example:				&Key: \\
						&Distractors: \\
\midrule
\textbf{CloseMatch}		&\\
						&Stem: In the context of Strategic Information Management, which one of the following triples belongs together the most?\\
Example:				&Key: Chief Information Officer – Department of Information management – IM Staff \\
						&Distractors: Labels of three resources connected in one of the distractor shapes in \cref{fig:intertwined}, such as
						Chief Information Officer – Strategic Gap – Corporate Strategy\\
\midrule
\textbf{}				&\\
						&Stem: \\
Example:				&Key: \\
						&Distractors: \\
\bottomrule
\end{tabulary}
\end{table}

@@

\subsection{Question Types}

TODO: Add the old question types, but only the b-versions (so no suffix is required in this paper)

@@

% set this as second strat to gain constistency to table 5 
\paragraph{definition}
The definition approach focuses on the question of which definition is fitting for a given term. 
To increase the difficulty of the strategy, the distractors are chosen to be at most two vertices away from the edge which represents the correct term, much like in the label-definition-type.

\paragraph{contains}
describe contains...

\paragraph{intertwined}

@@

\begin{table}
\begin{tabulary}{\textwidth}{LLLL}
\toprule
Question			&Correct answer	&Distractor 1	&Distractor 2\\ 
\midrule
In the context of Strategic IM, which one of the following triples belongs together the most? &Chief Information Officer -- Department of Information management -- IM Staff & Chief Information Officer -- Strategic Gap -- Corporate Strategy & Chief Information Officer -- Ticket Evaluation -- Project Monitoring \\
\midrule
In the context of Strategic IM, which one of the following triples belongs together the most? & IM -- IT Service Management -- Operational IM & IM -- Tactical Management of Information Systems -- Information System & IM -- methodology of IM -- Operational Management of Information Systems\\
\midrule
In the context of CIOX, which one of the following triples belongs together the most & Chief Information Officer -- Jour Fixe Execution -- Project Monitoring & Chief Information Officer -- Project Risk -- Strategic HIS Planning & Chief Information Officer -- IT General Ledger Account Planning -- Project Portfolio \\
\midrule
In the context of CIOX, which one of the following triples belongs together the most & Chief Information Officer -- Project Presentation -- Project Waitlist & Chief Information Officer -- Strategic IM Planning -- Project Manager & Chief Information Officer -- Project Priorisation -- Project Web Site \\
\bottomrule
\end{tabulary}
\caption{Examples of generated \emph{intertwined}-questions and answers.}
\label{tab:intertwined}
\end{table}

Intertwined focuses on the connectivity of the knowledge graph.
In each answer, three related concepts are given.
The correct answer is the one where all concepts are directly connected with each other, that is, they form a triangle in the graph, see \cref{fig:intertwined}.
The distractors should then not form this triangle.
In the difficult variation of the distractor, one of the three concept pairs is directly connected, one has a shortest path of length 2 and the third one has neither.
In this easier variation, two concepts pairs are connected with a shortest path of length 2 instead.
Examplse are given in \cref{tab:intertwined}.

@@

The \emph{occurence} question type is a specialization of \emph{closeMatch}, where the student has to choose whether a term occurs in~\cite{ob},~\cite{bb}, in both textbooks or neither of them.
Exemplary questions are given in \cref{tab:occurence}.
%mögliche Frage ist hier: \enquote{In which books does the term \emph{Chief Information Officer} occur?}.
The context of the questions can be augmented with the definitions of the concepts.

@@

@@

%\section{Acknowledgments}
%This work is supported by the DFG (German Research Foundation) under the Projects SNIK, grant no. 1605/7-1 and 1387/8-1, as well as HITO, grant no. WI 1605/11-1 and I3726-N31.
%We thank the publishers ... and ... for granting us permission to publish the subontologies based on the textbooks \citet{bb,ob,he} under an open license.
%\nocite{*} 
\todo{FJ: Hmmm, ziemlich selbstreferenziell. Brauchen wir da wirklich so viele Publikationen von uns? Welche anderen könnte man noch einbringen? Ich schaue auch mal, was mir so über den Weg läuft.}
%\bibliographystyle{ios1}
\bibliographystyle{vancouver}
\bibliography{paper,snik,relatedwork}
%\section{Notes to Reviewers}
%This paper includes and extends text and figures from:
%\citet{snikgraph}
\end{document}

>>>>

\begin{table}[t]
\caption{Quiz question templates with examples. When not otherwise noted, distractors are wrong answers that are neighbors of degree at most 2 of the correct answer.}
\label{tab:templates}
\centering
\begin{tabulary}{\columnwidth}{lL}
\toprule
\textbf{Template}	&\textbf{Description}\\
\midrule
\textbf{Subject}		&Ask for the subject of a (subject, relation, object) triple given the relation and object.\\
%						&Distractors are labels of other classes (of the same type) that \emph{are not} related via the same relation to the same object but which are connected to the correct answer with a path of length at most 2.\\
Stem					&\emph{Who is \emph{responsible for} \emph{Medical Admission}?}\\
Key						&\emph{Physician}\\
Distractors				&\emph{Surgeon}, \emph{Health Care Professional}, \emph{Senior Physician}\\
\midrule
\textbf{Object}			&Ask for the object of a (subject, relation, object) triple given the subject and relation.\\
Stem					&\emph{The \emph{Specification Team} is \emph{responsible for}}$\ldots$\\
Key						&\emph{Functional Specification Document}\\
Distractors: 			&\emph{Project Team Member}, \emph{Sponsor}, \emph{Defining Project Organization}\\
\midrule
\textbf{Definition}		&Ask for the class that fits the given textbook definition.\\
Stem					&\emph{What is defined by this?}\\
						&\enquote{X assures a defined quality of all processes and outcomes of the hospital}\\
Key						&\emph{Internal Quality Management}\\
Distractors				&\emph{Activity}, \emph{Complaint}, \emph{Diagnosis}\\
\midrule
\textbf{Intertwined}	&The correct answer is a triangle in the graph. The distractors instead form different shapes based on the difficulty. See \cref{fig:intertwined}.\\
Stem					&In the context of Strategic Information Management, which one of the following triples belongs together the most?\\
Key						&\emph{Chief Information Officer -- Department of Information management -- IM Staff}\\
Distractor 1			&\emph{Chief Information Officer -- Strategic Gap -- Corporate Strategy}\\
Distractor 2			&\emph{Chief Information Officer -- Ticket Evaluation -- Project Monitoring}\\
\midrule
\textbf{CloseMatch}		&\\
Stem \\
Key \\
Distractors \\
\midrule
\textbf{Label-Definition}	&Present different definitions and ask, which of them fits the given entity.\\
Stem					&\emph{How is \enquote{Chief Executive Officer} defined?}\\
Key						&\emph{Responsible for setting and carrying out the strategic plans and policies of an enterprise.}\\
Distractors				&labels of entities within a path length of at most 2, e.g. \emph{Anyone who has direct or indirect influence on or interest in a component of an information system.}\\
\midrule
\textbf{}				&\\
						&Stem: \\
Example:				&Key: \\
						&Distractors: \\
\bottomrule
\end{tabulary}
\end{table}

@@

\subsection{Question Types}
\iffalse
TODO: Add the old question types, but only the b-versions (so no suffix is required in this paper)

@@

% set this as second strat to gain constistency to table 5 
\paragraph{definition}
The definition approach focuses on the question of which definition is fitting for a given term. 
To increase the difficulty of the strategy, the distractors are chosen to be at most two vertices away from the edge which represents the correct term, much like in the label-definition-type.
\fi

@@

\iffalse
\begin{table}
\begin{tabulary}{\textwidth}{LLLL}
\toprule
Question			&Correct answer	&Distractor 1	&Distractor 2\\ 
\midrule
In the context of Strategic IM, which one of the following triples belongs together the most? &Chief Information Officer -- Department of Information management -- IM Staff & Chief Information Officer -- Strategic Gap -- Corporate Strategy & Chief Information Officer -- Ticket Evaluation -- Project Monitoring \\
\midrule
In the context of Strategic IM, which one of the following triples belongs together the most? & IM -- IT Service Management -- Operational IM & IM -- Tactical Management of Information Systems -- Information System & IM -- methodology of IM -- Operational Management of Information Systems\\
\midrule
In the context of CIOX, which one of the following triples belongs together the most & Chief Information Officer -- Jour Fixe Execution -- Project Monitoring & Chief Information Officer -- Project Risk -- Strategic HIS Planning & Chief Information Officer -- IT General Ledger Account Planning -- Project Portfolio \\
\midrule
In the context of CIOX, which one of the following triples belongs together the most & Chief Information Officer -- Project Presentation -- Project Waitlist & Chief Information Officer -- Strategic IM Planning -- Project Manager & Chief Information Officer -- Project Priorisation -- Project Web Site \\
\bottomrule
\end{tabulary}
\caption{Examples of generated \emph{intertwined}-questions and answers.}
\label{tab:intertwined}
\end{table}
\fi

\iffalse
Intertwined focuses on the connectivity of the knowledge graph.
In each answer, three related concepts are given.
The correct answer is the one where all concepts are directly connected with each other, that is, they form a triangle in the graph, see \cref{fig:intertwined}.
The distractors should then not form this triangle but a different shape based on the difficulty.
In the difficult variation of the distractor, one of the three concept pairs is directly connected, one has a shortest path of length 2 and the third one has neither.
In this easier variation, two concepts pairs are connected with a shortest path of length 2 instead.

@@

The \emph{occurence} question type is a specialization of \emph{closeMatch}, where the student has to choose whether a term occurs in~\cite{ob},~\cite{bb}, in both textbooks or neither of them.
Exemplary questions are given in \cref{tab:occurence}.
%mögliche Frage ist hier: \enquote{In which books does the term \emph{Chief Information Officer} occur?}.
The context of the questions can be augmented with the definitions of the concepts.
\fi

@@

\label{tab:templates} subclasses and superclasses
because of OWL punning entities are individuals but also classes and can have superclasses and subclasses
subclasses of the correct answer are semantically correct because subclasses are subsets
superclasses on the other hand are only partially correct because the relation only holds for the subclass
example who is responsible for medical admission: Health Care Professional - Physician - Senior Physician
however SPARQL endpoint doesnt do inferencing so it will not mark that as correct
we could add the transitive hull for such triples but we think it is good like this, it increases the difficulty and you need to choose the most general correct answer

@@

%\section{Acknowledgments}
%This work is supported by the DFG (German Research Foundation) under the Projects SNIK, grant no. 1605/7-1 and 1387/8-1, as well as HITO, grant no. WI 1605/11-1 and I3726-N31.
%We thank the publishers ... and ... for granting us permission to publish the subontologies based on the textbooks \citet{bb,ob,he} under an open license.
%\nocite{*} 
%\bibliographystyle{ios1}
\bibliographystyle{vancouver}
\bibliography{paper,snik,relatedwork}
\end{document}
